Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-11-03 demystify.tex
updates

Faculty often receive ``cold'' e-mails from prospective students. Most of the time, we ignore these emails, but on some rare occasions, we do answer them. So how to write an email that gets our attention?

@@

However, this is not why we ``ghost'' you and provide no response.  It is because we want to avoid misunderstandings.  A response (\autoref{sec:interpreting-response}), no matter how clear we think it is, might be misinterpreted by the student.  For example, if we say we are not taking students but still (strongly) encourage to apply, then the student might take it as a positive sign of admission. Or if we say we are not interested, the student might take it as a personal rejection and not apply at all.  So it is not because we are too busy to reply, but because we do not want misunderstandings and have to deal with them later.

>>>>

Faculty often receive ``cold'' e-mails from prospective students. Most of the time, we ignore these emails (\autoref{sec:busy}), but on some rare occasions, we do answer them. So how to write an email that gets our attention?

@@

However, this is not why we ``ghost'' you and provide no response (\autoref{sec:interpreting-response}).  It is because we want to avoid misunderstandings.  A response (\autoref{sec:interpreting-response}), no matter how clear we think it is, might be misinterpreted by the student.  For example, if we say we are not taking students but still (strongly) encourage to apply, then the student might take it as a positive sign of admission. Or if we say we are not interested, the student might take it as a personal rejection and not apply at all.  So it is not because we are too busy to reply, but because we do not want misunderstandings and have to deal with them later.
